MS Keyrun Species, Environment, Data Formats

### 2020-07-08 docs/SpeciesEnvDat2.Rmd
start on species list with full rpath table

Current species groups in the GB Rpath model:
```{r rpathspp, message=FALSE}

@@

rpathspp <- species %>%
  select(RPATH, COMNAME, SCINAME, SVSPP) %>%
  filter(RPATH != "") %>%
  distinct()

aggs <- rpathspp %>%
  count(RPATH, sort = TRUE, name = "Nspp") %>%
  filter(Nspp > 1)

singlespp <- anti_join(rpathspp, aggs) %>%
  mutate(Nspp = 1)

rpathlist <- full_join(singlespp, aggs)

datatable(rpathlist, rownames = FALSE, 
          options = list(pageLength = 25, 
                         order = list(list(0, 'asc'))
          ))

@@

@@

## Meeting minutes (old link)

>>>>

Current species groups in the GB Rpath model:
```{r rpathspp}

@@

rpathspp <- species %>%
  select(RPATH, COMNAME, SCINAME, SVSPP) %>%
  distinct()

  #count(SVSPP, RPATH, sort = TRUE, name = "Nspp")

datatable(rpathspp, rownames = FALSE, options = list(pageLength = 25))

@@

### REVISE BELOW HERE FOR UPDATED SURVEY

@@

We had `r nrow(responses)` responses.

### Years (start-end)

Responses:
```{r}
startend <- data.frame(Start = responses$StartYear,
                       End = responses$EndYear)
knitr::kable(startend, booktabs=TRUE)
```

```{r} 
knitr::kable(responses$Rationale.for.start.time, col.names = "Start year rationale", booktabs=TRUE)
```

```{r}
knitr::kable(responses$Rationale.for.end.time, col.names = "End year rationale", booktabs=TRUE)
```

### Seasons (fall/spring surveys? fishery seasons?)

Responses:
```{r seasons}

seasons <- responses %>%
  select(SurvSeason, FishSeason) %>%
  gather(key = SurvFish, value = "Season") %>%
  arrange(Season)

ggplot(seasons, aes(Season, fill=SurvFish)) + 
  geom_bar() +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))#+ 
  #theme(axis.text.x = element_text(angle = 90))

```{r} 
knitr::kable(responses$Rationale.for.survey.temporal.resolution, col.names = "Survey season rationale", booktabs=TRUE)
```

```{r} 
knitr::kable(responses$Rationale.for.fishery.temporal.resolution, col.names = "Fishery season rationale", booktabs=TRUE)
```

### Spatial footprint (Georges Bank defined how)

Responses:
```{r space}

ggplot(responses, aes(SpatialGB)) + 
  geom_bar() +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 35))#+

```{r} 
knitr::kable(responses$Rationale.for.spatial.definition, col.names = "Spatial Rationale", booktabs=TRUE)
```

## Meeting minutes
